---
title: "Public Transit: Fixing the Pains of Traffic?-  Graphs"
author: "Kunaal Raghav"
format: pdf
editor: visual
---

## Installation of Packages

In order to run the code properly, please install and library the packages in the following code chunk. If you don't have the requisite packages installed, please delete the comment in front of the "install.package" line ( the #), install once, and then delete the those lines of code. Only keep the "library()" codes

```{r}
#install.packages("tidyverse")
library(tidyverse)
library(readxl)
```

## Overview of Data Sources

Data for each of the three public transit systems was obtained through a variety of different sites. Each of sections detail where the sources were obtained, what the sources are , what they measure, how they look like, and present graphs that will be detailed in the upcoming policy section

## DC Metro's System

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
Sources<- read_xlsx("C:/Users/xbox/OneDrive/Collect Files/Collect Files/MPP- Graduate  AU/Graduate Paperwork/PUAD 650/Boardings by Month.xlsx")

```

You can add options to executable code like this

```{r}
#| echo: false


ggplot(Sources, aes(x = Year, y = TF2)) +
  geom_col(fill = "steelblue") +
  labs(
    title = "Ridership per Year",
    x = "Year",
    y = "Ridership (in the the Thousands)"
  )





```

The `echo: false` option disables the printing of code (only output is displayed).
